# pre-class


Make sure you commit this often with meaningful messages. 



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Read the source code for each of the following three functions, puzzle out what they do, and then brainstorm better names.

```
f1 <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
f2 <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
f3 <- function(x, y) {
  rep(y, length.out = length(x))
}
```
```{r}
has_prefix <- function(string, prefix) {
  substr(string, 1, nchar(prefix)) == prefix
}
has_prefix(c("hey_ho", "another_pre"), "hey")
remove_last <- function(x) {
  if (length(x) <= 1) return(NULL)
  x[-length(x)]
}
remove_last(c(1, 2, 3))
convert_length <- function(x, y) {
  rep(y, length.out = length(x))
}
convert_length(1:10, 1:3)

```


2. Compare and contrast rnorm() and MASS::mvrnorm(). How could you make them more consistent?

```{r}
#I could start by crating a function that takes the rnorm(n, mean, sd), which uses the standard deviation for the spread.
#MASS:mvrnorm(n, mu, Sigma), is a multivariate equivalent, which uses the variance-covariance matrix for the spread. In the univariate case, Sigma is the variance.
```

3. Use `lapply()` and an anonymous function to find the coefficient of variation (the standard deviation divided by the mean) for all columns in the mtcars dataset. 
```{r}
lapply(mtcars, function(x) sd(x) / mean(x))
```


4. Use vapply() to:
    a. Compute the standard deviation of every column in a numeric data frame.
    b. Compute the standard deviation of every numeric column in a mixed data frame. (Hint: you’ll need to use vapply() twice.)
```{r}
#a
vapply(mtcars, sd, numeric(1))
#b
vapply(mtcars[vapply(df,  is.numeric, logical(1))], sd, numeric(1))
```

